### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	09:10:45	(Tue18.Mar)
la2pdf commit - 2014:03:18	09:36:13	(Tue18.Mar)

\ai{Yes! This is likely the reason. Thank you for pointing this out. This will be added to the conclusions.}

@@

\q{I suspect many readers of the paper will not have the same assumptions as the authors, if they are not processing high-frequency narrowband signals with undersampled arrays. I see this disconnect between low-frequency passive processors and mid-frequency active processors, but the gap to imaging sonars is even greater. I venture that the authors can greatly broaden the appeal of their paper by addressing the questions I pose below.}

>>>>

\ai{Yes! This is likely the reason. Thank you for pointing this out. This is now added to the discussion.}

@@

\q{I suspect many readers of the paper will not have the same assumptions as the authors, if they are not processing high-frequency narrowband signals with undersampled arrays. I see this disconnect between low-frequency passive processors and mid-frequency active processors, but the gap to imaging sonars is even greater. I venture that the authors can greatly broaden the appeal of their paper by addressing the questions I pose below.}\\[-.5\baselineskip]

\ans{It is clear we had to state this better upfront. In the 5th paragraph of the introduction we now explain that our system is a well sampled wideband sonar.}
